Catastrophic Goodhart: regularizing RLHF with KL divergence does not mitigate heavy-tailed reward misspecification

### 2024-10-24 paper/main.tex
fix wording of theorem 2
In statement of Theorem 4, add the assumption that utility is unbounded.

\begin{theorem}
    \label{thm2} However, if \(V\) is light-tailed and \(d = D_{KL}(P \| Q)\) is bounded, then
    \(\mathbb E_P[V]\) is bounded, and \(\mathbb E_P[V] - \mathbb E_Q[V] \to 0\) as
    \(d \to 0\).
    \end{theorem}

@@

\subsection{If V is light-tailed, \texorpdfstring{$\mathbb E_P[V]\! -\! E_Q[V] \to 0$}{} as \texorpdfstring{$D_{KL}\! \to\! 0$}{}}

@@

\begin{theorem}
\label{thm4} If \(U=X+V\) with \(X\) and \(V\) both
light-tailed, and the distribution of U is continuous, and
\(\pi^*(\beta) \triangleq \arg \max_\pi \mathbb E[U(\pi)] - \beta D_{KL}(\pi, \pi_0)\),
then \(\lim_{\beta \to 0^+} \mathbb E[V(\pi^*(\beta))] = \infty\).
\end{theorem}

@@

\newtheorem*{theorem4}{Restatement of Theorem \ref{thm4}}
\begin{theorem4}
If \(U=X+V\) with \(X\) and \(V\) both
light-tailed, and the distribution of U is continuous, and
\(\pi^*(\beta) \triangleq \arg \max_\pi \mathbb E[U(\pi)] - \beta D_{KL}(\pi, \pi_0)\),
then \(\lim_{\beta \to 0^+} \mathbb E[V(\pi^*(\beta))] = \infty\).
\end{theorem4}

>>>>

\begin{theorem}
    \label{thm2} However, if the distribution $Q$ is light-tailed and \(d = D_{KL}(P \| Q)\) is bounded, then
    \(\mathbb \mu_P \) is bounded, and \(\mu_P - \mu_Q \to 0\) as
    \(d \to 0\).
    \end{theorem}

@@

@@

\begin{theorem}
\label{thm4} If \(U=X+V\) with \(X\) and \(V\) both
light-tailed and \(V\) unbounded, and the distribution of U is continuous, and
\(\pi^*(\beta) \triangleq \arg \max_\pi \mathbb E[U(\pi)] - \beta D_{KL}(\pi, \pi_0)\),
then \(\lim_{\beta \to 0^+} \mathbb E[V(\pi^*(\beta))] = \infty\).
\end{theorem}

@@

\newtheorem*{theorem4}{Restatement of Theorem \ref{thm4}}
\begin{theorem4}
    If \(U=X+V\) with \(X\) and \(V\) both
    light-tailed and \(V\) unbounded, and the distribution of U is continuous, and
    \(\pi^*(\beta) \triangleq \arg \max_\pi \mathbb E[U(\pi)] - \beta D_{KL}(\pi, \pi_0)\),
    then \(\lim_{\beta \to 0^+} \mathbb E[V(\pi^*(\beta))] = \infty\).
\end{theorem4}
